This is an example of article title

### 2025-10-26 paper/paper.tex
Start structuring the paper and start the introduction.

@@

\section{Notation}

\section{The interface}
\subsection{Lie groups}

@@

\section{Implemented Lie groups}
\begin{table}[tbp]
    \centering
    \caption{Implemented Lie groups in \texttt{LieGroups.jl} as of version 0.1.6}
    \begin{tabular}{@{}lll@{}}
        \toprule
        \textbf{Group} & \textbf{Symbol} & comment/code\\
        \midrule
        \verb|CircleGroup()| & \(\mathbb{S}^1\) & 3 representations \\
        \verb|GeneralLinearGroup(n, F)| & \(\mathrm{GL}(n, \mathbb{F})\) & $\mathbb{F} \in \{\mathbb{R}, \mathbb{C}\}$\\
        \verb|HeisenbergGroup(n)| & \verb|H(n)| \\
        \verb|OrthogonalGroup(n)| & \(\mathrm{O}(n)\) &\\
        \midrule
        \verb|PowerLieGroup(G, n)| & \(\mathcal G^n\) & \verb|G^n|\\
        \verb|ProductLieGroup(G1, G2,...)| & \(\mathcal G_1 \times \mathcal G_2 \times \ldots\) & \verb|G1| $\times$ \verb|G2| $\times$ \ldots\\
        Semidirect product group & \(\mathcal G_1 \ltimes \mathcal G_2\) & \verb|G1| $\ltimes$ \verb|G2|\\
                                 & \(\mathcal G_1 \rtimes \mathcal G_2\) & \verb|G1| $\rtimes$ \verb|G2|\\
        \midrule
        \verb|SpecialEuclideanGroup(n)| & \(\mathrm{SE}(n)\) & \\
        \verb|SpecialGalileanGroup(n)| & \(\mathrm{SGal}(n)\) &  \\
        \verb|SpecialLinearGroup(n, F)| & \(\mathrm{SL}(n, \mathbb{F})\) & $\mathbb{F} \in \{\mathbb{R}, \mathbb{C}\}$\\
        \verb|SpecialOrthogonalGroup(n)| & \(\mathrm{SO}(n)\) &  \\
        \verb|SpecialUnitaryGroup(n)| & \(\mathrm{SU}(n)\) & \\
        \midrule
        \verb|SymplecticGroup(n)| & \(\mathrm{Sp}(2n)\) & \\
        \verb|TranslationGroup(n; field=|$\mathbb{F}$\verb|)| & \(\mathbb{F}^n\) & $\mathbb{F} \in \{\mathbb{R}, \mathbb{C}, \mathbb{H}\}$\\
        \verb|UnitaryGroup(n)| & \(\mathrm{U}(n)\) & \\
        \bottomrule
    \end{tabular}
\end{table}

\section{An example how to use {\texttt{LieGroups.jl}}}

>>>>

In many situations, one encounters data that does not reside in a vector space.
For example in robotics, the configuration space of a rigid body in three-dimensional
space is given by the special Euclidean group \(\mathrm{SE}(3)\),
consisiting of all translations and rotations.
A subset of these is the space of rotations, given by the special orthogonal group \(\mathrm{SO}(3)\),
or more generally \(\mathrm{SO}(n)\) in \(n\)-dimensional space.

These spaces are examples of Lie groups, formally defined as a smooth manifold equipped with a group structure.

The package \verb|LieGroups.jl| aims to provide an easy access to using Lie groups within
the Julia programming language \cite{bezanson2017julia} by providing an interface to define
and work with Lie groups, as well as providing a library of Lie groups, that can directly be used.

This paper aims to provide an overview of the main features of \verb|LieGroups.jl|.
After introducing the necessary notation in Section~\ref{sec:Notation},
we present the interface in Section~\ref{sec:Interface}, split into the Lie group, the Lie algebra, and group actions.
In Section~\ref{sec:LieGroups}, we present an overview of currently implemented Lie groups.
Finally, in Section~\ref{sec:Example}, we demonstrate how to get started and use \verb|LieGroups|.

\section{Notation}\label{sec:Notation}

\begin{figure}
    \centering
    \includegraphics[width=0.1875\textwidth]{logo.png}
    \caption{Logo of \texttt{LieGroups.jl}.}
    \label{fig:liegroups_logo}
\end{figure}

\section{The interface}\label{sec:Interface}

@@

\subsection{Lie groups}

@@

\section{Implemented Lie groups}\label{sec:LieGroups}
\begin{table}[tbp]
    \centering
    \caption{Implemented Lie groups in \texttt{LieGroups.jl} as of version 0.1.6}
    \begin{tabular}{@{}lll@{}}
        \toprule
        \textbf{Group} & \textbf{Symbol} & comment/code\\
        \midrule
        \verb|CircleGroup()| & \(\mathbb{S}^1\) & 3 representations \\
        \verb|GeneralLinearGroup(n, F)| & \(\mathrm{GL}(n, \mathbb{F})\) & $\mathbb{F} \in \{\mathbb{R}, \mathbb{C}\}$\\
        \verb|HeisenbergGroup(n)| & \verb|H(n)| \\
        \verb|OrthogonalGroup(n)| & \(\mathrm{O}(n)\) &\\
        \midrule
        \verb|PowerLieGroup(G, n)| & \(\mathcal G^n\) & \verb|G^n|\\
        \verb|ProductLieGroup(G1, G2,...)| & \(\mathcal G_1 \times \mathcal G_2 \times \ldots\) & \verb|G1| $\times$ \verb|G2| $\times$ \ldots\\
        Semidirect product group & \(\mathcal G_1 \ltimes \mathcal G_2\) & \verb|G1| $\ltimes$ \verb|G2|\\
                                 & \(\mathcal G_1 \rtimes \mathcal G_2\) & \verb|G1| $\rtimes$ \verb|G2|\\
        \midrule
        \verb|SpecialEuclideanGroup(n)| & \(\mathrm{SE}(n)\) & \\
        \verb|SpecialGalileanGroup(n)| & \(\mathrm{SGal}(n)\) &  \\
        \verb|SpecialLinearGroup(n, F)| & \(\mathrm{SL}(n, \mathbb{F})\) & $\mathbb{F} \in \{\mathbb{R}, \mathbb{C}\}$\\
        \verb|SpecialOrthogonalGroup(n)| & \(\mathrm{SO}(n)\) &  \\
        \verb|SpecialUnitaryGroup(n)| & \(\mathrm{SU}(n)\) & \\
        \midrule
        \verb|SymplecticGroup(n)| & \(\mathrm{Sp}(2n)\) & \\
        \verb|TranslationGroup(n; field=|$\mathbb{F}$\verb|)| & \(\mathbb{F}^n\) & $\mathbb{F} \in \{\mathbb{R}, \mathbb{C}, \mathbb{H}\}$\\
        \verb|UnitaryGroup(n)| & \(\mathrm{U}(n)\) & \\
        \bottomrule
    \end{tabular}
\end{table}

\section{An example how to use {\texttt{LieGroups.jl}}}\label{sec:Example}
